%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To compile, run: lualatex cv.tex

% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.1
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[]{friggeri-cv-a4}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{carolina}{brañas}{data scientist} % Your name and current job title/field

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Copenhagen, Capital Region 2300
Denmark
~
+34 644 004 477
+45 60 90 73 33
~
\href{mailto:carobrasor@gmail.com}{email}
\href{https://carobs9.github.io/}{website}
\href{https://www.linkedin.com/in/carolinabranas/}{linkedin}
\href{https://github.com/carobs9}{github}
\section{languages}
spanish: mother tongue
english \& galician: fluency
\section{programming}
Python, SQL, HTML, CSS
Git
\end{aside}

%----------------------------------------------------------------------------------------
% ABOUT ME SECTION
%----------------------------------------------------------------------------------------

\section{about me}

Data scientist particularly interested in the fields of machine learning, network analysis, natural language processing and urban mobility. \\
Eager to use these tools to find relevant solutions to actual problems.


%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2022--2025}
{Masters {\normalfont of Social Data Science}}
{The University of Copenhagen, Denmark}
{\emph{Mobility and Income Segregation in Madrid, Spain} \\ This thesis explores the relationship between income inequality and urban mobility in the city of Madrid.}

%------------------------------------------------

\entry
{2018--2022}
{Bachelor {\normalfont of Business}}
{Cardinal Stritch University, United States}
{Specialization in Marketing}

%------------------------------------------------

\entry
{2018--2022}
{Minor {\normalfont of Computer Science}}
{Cardinal Stritch University, United States}

\end{entrylist}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Part Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2025--Now}
{University of Copenhagen, Economics Department}
{Copenhagen, Denmark}
{\emph{Research Assistant in Data Science} \\
Continued working along a team of researchers for the project \emph{Shocking Religion}, which examines the impact of religion on economic factors using shocks to religion as natural experiments. \\
Detailed achievements:
\begin{itemize}
\item Worked collaboratively into building, finetuning and deploying Transformer models for classification tasks.
\item Developed advanced topic modelling techniques (mainly Transformer models) to analyze textual data from religious non-profit organizations. This project included building preprocessing pipelines, model training, evaluation and visualization.
\item Gathered, processed, and performed time-series analysis on county level U.S. data, covering several economic factors (GDP, population, public spending, poverty rates, etc.).
\item Integrated geospatial raster and polygon data to assess and visualize earthquake exposure across global regions.
\end{itemize}}

%------------------------------------------------

\entry
{2023--2024}
{Above Sports}
{Copenhagen, Denmark}
{\emph{Data Analyst} \\
Worked as a data analyst in Above Sports, a sponsorship measuring platform.
Detailed achievements:
\begin{itemize}
\item Worked collaboratively with the data science team to improve processes automation and overall product performance.
\item Built automation pipelines for machine learning tasks.
\item Built computer vision machine learning models to improve the company's logo detection tool.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Paid Internships and Student Jobs}

\begin{entrylist}

\entry
{2024--2025}
{University of Copenhagen, Economics Department}
{Copenhagen, Denmark}
{\emph{Research Assistant} \\
Collaborated along a team of researchers for the project \emph{Shocking Religion}, which examines the impact of religion on economic factors using shocks to religion as natural experiments. \\}

%------------------------------------------------

\entry
{2021--2022}
{Crescendo Collective LLC}
{Milwaukee, United States}
{\emph{Marketing Strategist} \\
Joined the digital marketing strategy team at Crescendo Collective, a global digital transformation and creative marketing agency.\\
Detailed achievements:
\begin{itemize}
\item Performed data analysis using Google Analytics and Google Ads data for clients, delivering detailed reports based on the findings.
\item Delivered internal and external research for the organization, such as competitors’ analysis and performance reports.
\item Developed page audits for the clients, as well as speed audits and research-based audits.
\item Worked with the data team on internal processes' automation pipelines.
\end{itemize}}

%------------------------------------------------

\entry
{2020--2021}
{Cardinal Stritch University}
{Milwaukee, United States}
{\emph{Student Ambassador} \\
Joined the digital marketing strategy team at Crescendo Collective, a global digital transformation and creative marketing agency.\\
Detailed achievements:
\begin{itemize}
\item Worked face to face with future clients and visitors.
\item Assisted admissions workers with main admissions events and fairs.
\item  Performed tours throughout the college campus for potential future students.
\item ctively participated in admissions events and the whole admissions process for future students.
\end{itemize}}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2018}
{Soccer and Educational Grant}
{Cardinal Stritch University}
{Awarded an academic and athletic scholarship for outstanding academic performance and soccer achievements to cover four years of bachelor's education, demonstrating discipline, teamwork, and commitment both in education and sports.}

%------------------------------------------------

\entry
{2018 to 2022}
{Dean's List}
{Cardinal Stritch University}
{Achieved Dean's List in every semester of my bachelors degree (Spring and Fall, 2018, 2019, 2020, 2021)
The Dean's List is comprised of a select group of students who have carried at least 12 credits and achieved a grade point average of
3.5 or above during a specific semester.}

%------------------------------------------------

\entry
{2022}
{Best Graduating GPA of Business Bachelor (Marketing specialization)}
{Cardinal Stritch University}
{Granted with the best graduating GPA (3.8/4.0) of the Bachelor of Science in Marketing of the 2022 class at the time of graduation}

%------------------------------------------------

\entry
{2018}
{CCAC Conference Tournament Champion}
{Chicagoland Collegiate Athletics Conference (CCAC)}

%------------------------------------------------

\entry
{2018}
{2018 NAIA National Tournament Sweet Sixteen Appearance}
{Chicagoland Collegiate Athletics Conference (CCAC)}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
% COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
% INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data science, website creation, mobility and urban planning, geospatial data, marketing \textbf{personal:} sports, nature 

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{document}
